An Effective Model of HL-60 Differentiation

### 2017-03-08 Paper_v2.tex
Completed table 2

	$R_{1}$ & RNA polymerase abundance & 75,000 & copies/cell & \cite{Jackson:2000aa,Zhao:2014aa} \\
	$R_{2}$ & Ribosome abundance & 1 x 10$^{6}$ & copies/cell & \cite{Freitas2004} \\
	$G_{i}$ & Characteristic gene abundance & 2 & copies/cell & this study\\
	$K_{X}$ & Saturation constant transcription & 4,600 & copies/cell & this study\\
	$K_{T}$ & Saturation constant translation & 100,000 & copies/cell & this study\\
	& & & & \\
	$t_{1/2,m}$ & characteristic mRNA half-life (transcription factor) & 2 & hr & \cite{Yang:2003aa} \\
	$t_{1/2,p}$ & characteristic protein half-life & 10 & hr & \cite{Doherty:2009aa} \\
	$\theta_{m,j}$ & characteristic mRNA degradation constant & 0.34 & hr$^{-1}$ & derived \\
	$\theta_{p,j}$ & characteristic protein degradation constant & 0.07 & hr$^{-1}$ & derived \\
	& & & & \\
	$t_{d}$ & HL-60 doubling time & 19.5 & hr & this study \\
	$\mu$ & growth rate & 0.035 & hr$^{-1}$ & derived \\
	$k_{d}$ & death rate & 0.10$\mu$ & hr$^{-1}$ & derived \\
	& & & & \\
	$e_{T}$ & elongation rate RNA polymerase & 6 & nt/s & \cite{Darzacq:2007aa} \\
	$e_{X}$ & elongation rate Ribosome & 5 & aa/s & \cite{Bostrom:1986aa} \\
	$L_{T,o}$ & characteristic gene length & 15,000 & nt & [REFHERE] \\
	$L_{X,o}$ & characteristic transcript length & 5,000 & nt & [REFHERE] \\
	$k_{T}$ & characteristic transcription rate & 1.44 & hr$^{-1}$ & derived \\
	$k_{X}$ & characteristic translation rate & 3.60 & hr$^{-1}$ & derived \\
	& & & & \\
	$D$	& Diameter of an HL-60 cell & 12.4 & $\mu$m$^{3}$ & \cite{Rosenbluth:2006aa} \\
	$f_{C}$ & cytoplasmic fraction & 0.51 & dimensionless & \cite{Rosenbluth:2006aa} \\

>>>>

	$R_{1}$ & RNA polymerase abundance & 75,000 & copies/cell & \cite{Jackson:2000aa,Zhao:2014aa} \\
	$R_{2}$ & Ribosome abundance & 1 x 10$^{6}$ & copies/cell & \cite{Freitas2004} \\
	$G_{i}$ & Characteristic gene abundance & 2 & copies/cell & this study\\
	$K_{X}$ & Saturation constant transcription & 4,600 & copies/cell & this study\\
	$K_{T}$ & Saturation constant translation & 100,000 & copies/cell & this study\\
	& & & & \\
	$t_{1/2,m}$ & characteristic mRNA half-life (transcription factor) & 2 & hr & \cite{Yang:2003aa} \\
	$t_{1/2,p}$ & characteristic protein half-life & 10 & hr & \cite{Doherty:2009aa} \\
	$\theta_{m,j}$ & characteristic mRNA degradation constant & 0.34 & hr$^{-1}$ & derived \\
	$\theta_{p,j}$ & characteristic protein degradation constant & 0.07 & hr$^{-1}$ & derived \\
	& & & & \\
	$t_{d}$ & HL-60 doubling time & 19.5 & hr & this study \\
	$\mu$ & growth rate & 0.035 & hr$^{-1}$ & derived \\
	$k_{d}$ & death rate & 0.10$\mu$ & hr$^{-1}$ & derived \\
	& & & & \\
	$e_{T}$ & elongation rate RNA polymerase & 6 & nt/s & \cite{Darzacq:2007aa} \\
	$e_{X}$ & elongation rate Ribosome & 5 & aa/s & \cite{Bostrom:1986aa} \\
	$L_{T,o}$ & characteristic gene length & 15,000 & nt & \cite{Meyers2004} \\
	$L_{X,o}$ & characteristic transcript length & 5,000 & nt & derived \\
	$k_{T}$ & characteristic transcription rate & 1.44 & hr$^{-1}$ & derived \\
	$k_{X}$ & characteristic translation rate & 3.60 & hr$^{-1}$ & derived \\
	& & & & \\
	$D$	& Diameter of an HL-60 cell & 12.4 & $\mu$m$^{3}$ & \cite{Rosenbluth:2006aa} \\
	$f_{C}$ & cytoplasmic fraction & 0.51 & dimensionless & \cite{Rosenbluth:2006aa} \\
